DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-06-01 ase2017/paper.tex
added section about CEGIS for control
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
described about the tool architecture
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\setcopyright{acmcopyright}
\acmDOI{10.475/123_4}
\acmISBN{123-4567-24-567/08/06}
\acmConference[EMSOFT '17]{The ACM SIGBED International Conference on Embedded Software }{October 15--20, 2017}{Seoul, South Korea}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

@@

@@

>>>>

%\setcopyright{acmcopyright}
%\acmDOI{10.475/123_4}
%\acmISBN{123-4567-24-567/08/06}
%\acmConference[ASE '17]{The ACM SIGBED International Conference on Embedded Software }{October 15--20, 2017}{Seoul, South Korea}
%\acmYear{2017}
%\copyrightyear{2017}
%\acmPrice{15.00}

@@

%---------------------------------------------------
\section{Counterexample-Guided Inductive Synthesis for Control Systems}
%---------------------------------------------------

\textcolor{red}{Cristina: can you please generalize our CEGIS implementation for control here?}

\textcolor{red}{We have to talk about the naive and AA back-ends, which are based on our CEGIS framework}

@@

\textcolor{blue}{The main development challenge related to \tool is the representation of the
closed-loop control system models, considering FWL effects, time discretization 
and quantization noise.  In particular, our implementation consists of $400$
lines of code related to MATLAB scripts, $585$ and $800$ lines of C code related to the
naive and abstract accelerator backends. In addition, there are $4000$ lines of C code
related to utility functions (e.g., interval and fixed-point arithmetic), $50$ lines
of code to parse MATLAB functions and there are approximately $20$
control system benchmarks to ensure the \tool's regression.  All those artifacts together
with documentation and videos are available in a public github repository,
which is located at \url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
